Group 9 Presentation

### 2021-12-06 presentation.Rmd
writing from representative trees

## Representative Tree

@@

paste("the overall fraction of correct predictions in the test dataset is :",(confm2[1,1]+confm2[2,2])/sum(confm2))
overall_log_reg <- (confm2[1,1]+confm2[2,2])/sum(confm2)
overall_log_reg

log_reg_mse <- mean((predicted2 - test$HeartDisease)^2) #MSE

>>>>

## Representative Tree
-Following the paper by  Banerjee, et al.(2011) and the package reprtree we can get a representative tree from the random forest.
-This tree is calculated using a measure of similarity in which 2 trees are similar if they have the same prediction for all observations.
-Using this idea on the random forest we get the following tree:

@@

 #MSE
